\texttt{TREE}: A package for modelling plant TRait Ecology and Evolution

### 2015-05-27 ms.tex
Update formatting to my usual template

\documentclass[]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{graphicx}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage[verbose,tmargin=2cm,bmargin=2cm,lmargin=3.5cm,rmargin=2.5cm]{geometry}

\usepackage{color}
\definecolor{grey}{rgb}{0.5, 0.5, 0.5}

\usepackage[unicode=true]{hyperref}
\urlstyle{same}  % don't use monospace font for urls
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={Daniel Falster, Rich FitzJohn, Mark Westoby},
            pdftitle={\texttt{TREE}: A package for modelling plant TRait Ecology and Evolution},
            colorlinks=true,
            citecolor=grey,
            urlcolor=grey,
            linkcolor=grey,
            pdfborder={0 0 0}}

\usepackage{lineno}
\linespread{2}

@@

\usepackage{authblk}
\title{\texttt{TREE}: A package for modelling plant TRait Ecology and Evolution}
\author[1]{Daniel S. Falster}
\author[1]{Richard G. FitzJohn}
\author[1]{Mark Westoby}
\affil[1]{Dept of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia}
\date{}

\usepackage[sort&compress]{natbib}
\bibliographystyle{mee}

@@

\begin{document}
\maketitle

\noindent A manuscript in consideration as a research paper for publication in MEE
as part of the Special Feature \emph{Demography beyond the Population}.

\linenumbers

\section{Abstract}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Population dynamics in forests are strongly size-structured:
  larger plants shade smaller plants while also expending
  proportionately more energy on building and maintaining woody stems.
  Although the importance of size-
  structure for demography is widely recognised, many mechanistic models
  either omit it entirely, or include only coarse approximations.
\item
  Here we introduce the \texttt{TREE} package (TRait Ecology and Evolution), an
  extensible framework for modelling plant demography across the entire
  life cycle via coupled differential equations. At its core, \texttt{TREE} is an
  individual-based mechanistic model where plant function is mediated by
  traits. Individuals from multiple species can be grown in isolation,
  in patches of competing plants, or in metapopulations under a
  disturbance regime. Dynamics within patches of competing plants are
  resolved using novel extensions of the Escalator Boxcar Train
  technique. Combined effects of trait-, size- and patch-structured
  dynamics are integrated into population level estimates of
  reproductive fitness.
\item
  \texttt{TREE} is presented as an open source \texttt{R} package and is
  available at
  \href{https://github.com/traitecoevo/tree}{github.com/traitecoevo/tree}.
  While accessed from R, the core routines in \texttt{TREE} are written in C++.
  The package provides for alternative physiologies and for
  hyper-parameterisation on the basis of plant functional traits. A
  detailed test suite is provided to ensure accuracy.
\item
  We provide worked examples illustrating \texttt{TREE}'s use to study the
  influence of functional traits on growth of individual plants, of
  whole patches and on assembly of ecological communities.
\end{enumerate}

>>>>

\documentclass[a4paper,11pt]{article}
\usepackage[osf]{mathpazo}
\usepackage{ms}
\usepackage[sort&compress]{natbib}
\raggedright

@@

\title{\texttt{TREE}: A package for modelling plant TRait Ecology and Evolution}
\author{Daniel S. Falster, Richard G. FitzJohn, and Mark Westoby}
\affiliation{
Department of Biological Sciences, Macquarie University, Sydney, NSW 2109, Australia\\
Email for correspondence: \texttt{daniel.falster@mq.edu.au}\\
A manuscript in consideration as a research paper for
publication in MEE as part of the Special Feature \emph{Demography
  beyond the Population}.}
\date{}

\bibliographystyle{mee}

@@

\mstype{Applications Note}
\runninghead{TREE}
% TODO: need more keywords here
\keywords{demography}

\begin{document}
\mstitlepage
\noindent
\parindent=1.5em
\addtolength{\parskip}{.3em}
\doublespacing
\linenumbers
\section{Summary}\label{abstract}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\itemsep1pt\parskip0pt\parsep0pt
\item
  Population dynamics in forests are strongly size-structured:
  larger plants shade smaller plants while also expending
  proportionately more energy on building and maintaining woody stems.
  Although the importance of size-
  structure for demography is widely recognised, many mechanistic models
  either omit it entirely, or include only coarse approximations.
\item
  Here we introduce the \texttt{TREE} package (TRait Ecology and Evolution), an
  extensible framework for modelling plant demography across the entire
  life cycle via coupled differential equations. At its core, \texttt{TREE} is an
  individual-based mechanistic model where plant function is mediated by
  traits. Individuals from multiple species can be grown in isolation,
  in patches of competing plants, or in metapopulations under a
  disturbance regime. Dynamics within patches of competing plants are
  resolved using novel extensions of the Escalator Boxcar Train
  technique. Combined effects of trait-, size- and patch-structured
  dynamics are integrated into population level estimates of
  reproductive fitness.
\item
  \texttt{TREE} is presented as an open source \texttt{R} package and is
  available at
  \href{https://github.com/traitecoevo/tree}{github.com/traitecoevo/tree}.
  While accessed from R, the core routines in \texttt{TREE} are written in C++.
  The package provides for alternative physiologies and for
  hyper-parameterisation on the basis of plant functional traits. A
  detailed test suite is provided to ensure accuracy.
\item
  We provide worked examples illustrating \texttt{TREE}'s use to study the
  influence of functional traits on growth of individual plants, of
  whole patches and on assembly of ecological communities.
\end{enumerate}
